A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing

### 2012-09-08 pathtracint_application_skeleton.tex
J'ai fait un include du fichier de Laurent dans le principal > il faut compiler le fichier principal.
Ajout de l'explication de la rendering equation et début de la partie sur la résolution de l'equation

\documentclass[final,envcountsame]{llncs}

%\usepackage{graphicx} %Pouvoir insérer des images
\usepackage{epsfig}
\usepackage{amsmath} %Permet d'utiliser une jolie panoplie de symboles mathématiques
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsfonts}

\def\mydef#1{{\em #1}}
\def\myem#1{{\em #1}}
\def\myvec#1{\vec{#1}}

\def\Nset{\mathbb{N}}
\def\Zset{\Z}
\def\Rset{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\def\allfaces#1{\mathbb{F}^{#1}}
\def\subfaces#1#2{\allfaces{#1}_{#2}}
\def\subcomplex#1#2{#1 \preceq #2}
\def\complex#1#2{\subcomplex{#2}{\allfaces{#1}}}
\def\cell#1{\hat{#1}}
\def\cellstrict#1{\hat{#1}^*}
\def\cont#1{\check{#1}}
\def\contstrict#1{\check{#1}^*}
\def\closure#1{#1^-}
\def\princ#1{#1^+}
\def\detach#1#2{#2 \oslash #1}
\def\attach#1#2{\mbox{\it{}Attach\/}(\cell{#1},#2)}
\def\mydim#1{\dim(#1)}
\def\type#1{\mbox{\it{}Dir\/}(#1)}
\def\orient#1{\mbox{\it{}Orient\/}(#1)}
\def\border#1{\mbox{\it{}CBorder\/}(#1)}
\def\suchthat{\;|\;}
\def\inter{\cap}
\def\union{\cup}
\def\dinterval#1#2{\{#1,\ldots,#2\}}
\newcommand{\Compl}[1]{\overline{#1}}
\def\finproof{\square}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\newcommand{\Card}[1]{|#1|}

\def\figpath#1{../../Images/EPS/#1}

\begin{document}

@@

\begin{equation}
L(x \rightarrow \Theta) = L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi) d\omega_\Phi
\end{equation}

It's actually this equation that a path tracer try to resolve. Let $O$ be the origine of the camera and $I$ the image we want to compute (a rectangle embedded in $\Rset^3$). Then the path tracing algorithm compute an approximation of the radiances $L(O \leftarrow \vec{OP})$, $\forall P \in I$.

@@

Parler rapidement de l'échantillonage et donner l'estimateur de monte carlo

@@

\subsection{Coarse irradiance estimation using curvilinear skeleton}

Décrire les heuristiques

\end{document}

>>>>

@@

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi) d\omega_\Phi \\
&= L_e(x \rightarrow \Theta) + L_r(x \rightarrow \Theta)
\end{align*}

This equation express an intuitive idea: the radiance produced by the point $x$ in the direction $\Theta$ is the sum of the emitted radiance and the reflected radiance.

The reflected radiance is computed by taking all the possible directions of the hemisphere around $x$ and integrate the incoming radiance along those directions scaled by a factor $f_r(x, \Theta \leftrightarrow \Phi) cos(N_x, \Phi)$.

The cosine is used to attenuate the radiance that arrive by a "direction rasante".

The $f_r$ function is called the \myem{bidirectional reflectance function} (BRDF) and express the exchange of radiance between the incoming direction $\Phi$ and the output direction $\Theta$. It has to respect three properties to be physically coherent:

\begin{itemize}
\item Helmotz reciprocity: $f_r(x, \Theta \leftrightarrow \Phi) = f_r(x, \Phi \leftrightarrow \Theta)$
\item Positivity: $f_r(x, \Theta \leftrightarrow \Phi) \geq 0$
\item Conservation of energy: $\int_{\Omega_x} f_r(x, \Theta \leftrightarrow \Phi) cos(N_x, \Phi) d\omega_\Phi \leq 1$
\end{itemize}

It's actually the rendering equation that a path tracer try to resolve. Let $O$ be the origin of the camera and $I$ the image we want to compute (a rectangle embedded in $\Rset^3$). Then the path tracing algorithm compute an approximation of the radiances $L(O \leftarrow \vec{OP})$, $\forall P \in I$.

@@

The rendering equation is a recursive integral equation. The integrand of the equation contains the radiance function that we must compute:

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_r(x, \Theta \leftrightarrow \Phi) L(x \leftarrow \Phi) cos(N_x, \Phi) d\omega_\Phi \\
&= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_r(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) cos(N_x, \Phi) d\omega_\Phi
\end{align*}

In practive it is impossible to compute anatically the integral, it has to be estimated. The most commonly used method is the Monte-Carlo integration that provide the following estimator for the integral:

\begin{equation*}
\langle L_r(x \rightarrow \Theta) \rangle = \frac{1}{N} \sum_{i = 1}^{N} \frac{f_r(x, \Theta \leftrightarrow \Phi_i) L(r(x, \Phi_i) \rightarrow -\Phi_i) cos(N_x, \Phi_i)}{p(\Phi_i)}
\end{equation*}

$p$ is a probability density function that is used to sample $N$ samples $(\Phi_i)_{i = 1...N}$ of the hemisphere $\Omega_x$.

This estimator is unbiased, it means that the esperance $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$.

% parler de la variance

@@
